---
title: "Corruption vs Development"
author: "Gabriel Correa"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Introduction

Recent political happenings have generated a number of questions about the use of public office for personal gain. Are these types of acts more or less like to occur in different governments and ,if so, under what circumstances? The inspiration for this project came from an article in the Economist titled "Corrosive Corruption". I will use data from Transparency International's Corruption Perceptions Index and the UN's Human Development Index to investigate this research question. 

#Data

The Corruption Perceptions Index provides data on about 180 countries and territories. This data is in the form of rankings based on information acquired from experts and business people. (www.transparency.org)
The second part of the data used comes from the UN's Human Development Index. The Human Development Index is a measure combining various factors such as health, wealth and education. (hdr.undp.org) 
The data have been aggregated by country. The analysis will focus on the relationship (if any) between Humand Development Index (HDI) and Corruption Perception Index (CPI). 

##Analysis

```{r Plot}
library(plotly)
library(data.table)
df <- fread('Economist_Data.csv', drop=1) #drop first column of data set.

p <- plot_ly(data=df, 
             x=~CPI, 
             y=~HDI,
             type = "scatter",
             mode = "markers",
             hoverinfo = "text",
             text = paste("CPI: ", df$CPI,
                          "<br>",
                          "HDI: ", df$HDI,
                          "<br>",
                          "Country: ", df$Country),
             marker = list(size=7),
             color = ~as.factor(Region)) %>%
  
  layout(title = "Corruption vs. Development Scatterplot",
         xaxis = list(title="Corruption Perception Index, (10=least corrupt)"),
         yaxis = list(title="Human Development Index, (1=Best)"))

p
```

Adding a trend line to the data above produces the following:

```{r Scatter plot with regression line}
library(plotly)
library(data.table)
df <- fread('Economist_Data.csv', drop=1) #drop first column of data set.
fit <- lm(HDI ~ CPI, data=df)
p <- plot_ly(data=df, 
             x=~CPI, 
             y=~HDI,
             type = "scatter",
             mode = "markers",
             hoverinfo = "text",
             text = paste("CPI: ", df$CPI,
                          "<br>",
                          "HDI: ", df$HDI,
                          "<br>",
                          "Country: ", df$Country),
             marker = list(size=7),
             color = ~as.factor(Region)) %>%
  add_lines(x=~CPI, y=fitted(fit))%>%
  
  layout(title = "Corruption vs. Development Scatterplot",
         xaxis = list(title="Corruption Perception Index, (10=least corrupt)"),
         yaxis = list(title="Human Development Index, (1=Best)"))

p
```

An $R^2$ value of about 0.49 was calculated for the fit line. 

#Conclusion
In conclusion, there does seem to be some evidence of a correlation between the Corruption Perception Index and the Human Development Index. 


##References



